### 2022-11-19 files/Overview.tex
Overview v1.2

@@

\subsubsection{Introduction}

>>>>

\section{Comparison of models}
This chapter introduces the models used in this dissertation.

Two models for a three-dimensional elastic solid are presented. These models are a cantilever and a free-free elastic body. A dimensionless variational form of the cantilever model is derived. General plane stress is discussed.

A model for a two-dimensional elastic solid is presented. The model is a cantilever elastic body. This model is a special case of plane stress of a three-dimensional elastic body. The model is given in a dimensionless variational form by simplification of the three-dimensional model.

Four models for a one-dimensional beam are presented using the Timoshenko beam theory are presented. The models are a cantilever, free-free, pinned-pinned and a suspended beam. A dimensionless variational form for the models are derived.

Two models for a Reissner-Mindlin plate are presented. The models are a cantilever and a rigidly clamped plate. A dimensionless variational form for the cantilever model is derived.

\subsection{Rod Theory}
**************

This chapter is a discussion and example of application of the theory presented in the article \cite{VV02}. This article concerns the existence and uniqueness of solutions of second order hyperbolic type problems. The models in this dissertation as such problems.\\

This chapter also concerns the idea of modal analysis. This is a method to find the natural frequencies of a system. This method is used later in the dissertation.

\subsection{Existence and uniqueness of solutions}
This section is a discussion of the theory presented in the article \cite{VV02}.

The authors define a general variational problem. This problem is defined on specific Hilbert spaces. Four assumptions are made in the article as well as some notation introduced.

\subsubsection{Main results for existence and uniqueness}
The main resuls of the article are given in this section. The results include existence and uniqueness of solutions for strong and weak damped models. The models in this dissertation are all weakly damped.

\subsubsection{First order system}
To prove the results, the approach of the authors are as follows.\\

The general variational problem is rewritten for a first order system of differential equations. This system is defined on a Hilbert space $H$. A operator $A$ is defined, and using the assumptions the authors prove that the operator $A$ is an infinitesimal generator of a $C_0$-semigroup of contractions with a domain in $H$.\\

Using this operator the authors rewrite the system of differential into the form $\displaystyle x' = Ax + f$. To be more precise, the system of first order system of differential equations can be written as an initial value problem.\\

The existence and uniqueness results for the first order system is easily proven with an initial value problem. The authors also prove that a solution of the first order system is also a solution to the general variational problem.\\

Using semi-group theory, a unnique solution for the initial value problem can be proved. The authors also provide the link between the solutions of the initial value problem and the general variational form. Thus proving the required results.

\subsection{Application: Timoshenko beam model}
As an example of the application of the theory, the weak variational form for the cantilever Timshenko beam is introduced. This weak variational problem is defined on complete product spaces.\\

The four assumptions of \cite{LVV09} are proved for this example model.

\subsection{Modal analysis}
*****************************************************************

\subsubsection{Timoshenko beam}
\subsubsection{General vibration problem}
\section{Finite element theory}

\subsection{Convergence of the Galerkin approximation}
In this Chapter, two convergence results related to the Finite Element Method is presented. This first result is the convergence of the Galerkin approximation of a second order hyperbolic type problem, presented in the article \cite{BV13}.\\

The second result concerns the convergence of the eigenvalue and eigenfunctions of a one-dimensional second order hyperbolic type problem when applying the Finite Element Method. This is presented in the textbook \cite{SF97}.

\subsubsection{Galerkin approximation}
In this section, the authors use the same general variational problem as presented in \cite{VV02} (Chapter 2). The authors assume that this general variational problem has a unique solution.\\

To start, the Galerkin approximation for the general variational problem is derived. The a unique solution is proved in \cite{BV13} when the forcing function $f$ is continuous.\\

Using the Finite Element Method matrices, the Galerkin approximation is rewritten as a system of ordinary differential equations.

\subsubsection{Error estimates}
Given that $u$ is a solution of the general variational problem, and $u^h$ is a solution to the Galerkin approximation, the authors define the error $e^h = u - u^h$.\\

The in \cite{BV13} the authors prove that this error can be made arbitrarily small by choosing a sufficiently small $h$, such that $u^h \rightarrow u$ as $h \rightarrow 0$. \cite{BV18} extends \cite{BV13} to include damping.\\

To obtain the error estimate, the authors split the error into two parts. The first part is a semi-dicrete problem and the second is a discrete problem. These two problems are investigated seperately.

In this section, the main results of \cite{BV13} are presented. The two assumptions made by the authors are also given.

In this section, the approach of the authors for determining the error estimates for the semi-discrete and fully discrete problems are presented.\\

\subsection{Convergence of eigenvalues in Finite Element Analysis}
*****************************************************************

\subsubsection{Eigenvalue problem for vibration problem}
\textbf{Problem GVarE}
\subsubsection{Interpolation theorem}
\subsubsection{Eigenvalue problem for our models*********}
\textbf{Notation}
\subsubsection{Convergence of the eigenvalues}
\subsubsection{Convergence of the eigenfunctions}
\subsection{Example}
\textbf{Problem 2D-1V}\\
\textbf{Test functions}
\subsubsection{Weak variational form}
\textbf{Problem 2D-1W}
\section{Timoshenko beam model}

In this chapter, the Timoshenko beam theory is explored further. In the first three sections, the theory and two examples of \cite{VV06} are given. 
\subsection{Eigenvalue problem}

In this article \cite{VV06}, the authors present a method for finding the exact eigenvalues and eigenfunctions for the Timoshenko beam theory. The method provides solutions for three cases where $\lambda <\alpha$, $\lambda =\alpha$ and $\lambda >\alpha$.\\

\subsection{Cantilever beam}
This is an example of the application of the theory on a cantilever Timoshenko beam. In this example some results in \cite{VV06} is verified and examples of the mode shapes are given.

This is an example of the application of the theory on a free-free Timoshenko beam.In this example some results in \cite{VV06} is verified and examples of the mode shapes are given.

\subsection{Suspended beam model}
The idea of a suspended Timoshenko is also discuss briefly.

\subsection{SP06}
In this section this section, the article \cite{SP06} is discussed. In this section, the authors obtain eigenvalues of a free-free Timoshenko beam by vibrating and measuring the natural frequencies of a real beam. This empirical data is then compared to the theoretical results of various methods, including the Finite Element Method.

In this last section, a example of the application of the Timoshenko beam model is presented. This section is a study of a technical report. In this report, the authors present a model for a cantilever Timoshenko beam with a tip body and elastic interfaces. This section also expands the numerical results of the report.\\

The variational form of the model is derived, and the Galerkin approximation follows. The Mixed Finite Element Method is applied to the model.\\

Using the Finite Element Method, the solution of the model is numerically calculated. Various results are given for different values of the parameters. The numerical results and figures confirms that the model behaves as expected.

\section{Finite element method}
This chapter is preperation for the final chapter in this dissertation. The finite element method to a cantilever version of each of the models in this dissertation. The goal of the chapter is to get a numerical formula to solve the eigenvalue problem for each model. The Timoshenko beam model is excluded from this chapter since an exact methd is already presented in chapter 4 (\cite{VV02}).\\

The model is assumed to have a rectangular cross-section and is in a cantilever configuration. The Galerkin approximation is derived and applying the finite element method, a numerical formula for solving the model problem is given.\\

In this numerical formula, the model problem is a system of linear equations. This system can be changed to obtain a numerical formula for teh eigenvalue problem.\\

\subsection{Three-dimensional elastic model}
Similar to above.

\subsection{Cantilever plate model}
Similar to above.

In this chapter, the validity of the models in this dissertation is investigated using numerical results. Specifically the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate is investigated.\\

In this case, the term validity refers to how well the model compares to a more realistic model.\\

All models are assumed to have a rectangular cross-section, are in a cantilever configuration and are made of the same isotropic material.\\

\subsection{Validity of the Timoshenko beam model}
This first section, is a discussion of the article \cite{LVV09}. In this article, the authors investigate the validity of the Timoshenko beam model. The authors compare the Timoshenko beam model to a more realistic two-dimensional beam model.\\

The comparison is made with the eigenvalues and eigenfunctions. From modal analysis it is known that the solution of the models are linear combinations of the eigenvalues and eigenfunctions.\\

The two-dimensional model also have eigenvalues that do not have a corresponding eigenvalue in the Timoshenko beam model. The authors call all matching eigenvalues beam-type eigenvalues.\\

The authors show that the Timoshenko beam model compare well to the two-dimensional model for long and short beams. The results of the article are verified and extra results are also calculated for the rest of this chapter.\\

In this section, the aricle \cite{LVV09} is extended to verify the validity of the two-dimensional elastic model. The two-dimensional elastic model is compared to a more realistic three-dimensional model.\\

The two dimensional model serves as a intermediate step between the Timoshenko beam model and the three-dimensional model.\\

The same approach of \cite{LVV09} is used to compare the two models. The result show that the two-dimensional model compare very well to the three-dimensional model, especially for beam problems.

The last section takes the idea of \cite{LVV09} and extends it to the Reissner-Mindlin plate model. The Reissner-Mindlin plate model is compared to a more realistic three-dimensional plate model.\\

******************************************************************\\

@@
